Time--Frequency Scattering Accurately Models Auditory Similarities Between Instrumental Playing Techniques

### 2020-10-12 paper/paper.tex
satisfactory performance -> high performance
GEH -> CEH in author initials

We see from the ablation study conducted above that each step of the proposed model is necessary for its satisfactory performance.
Among other things, it indicates the joint time--frequency scattering transform itself should not be used directly for similarity comparisons, but is best augmented by a learned stage.
This explains the relative success of such models \cite{lostanlen2018jasmp,lostanlen2018extended} over others where distances on raw scattering coefficients were used for judging audio similarity.

@@

VL provided guidance in the design of the computational experiments and was a major contributor in writing the manuscript. GEH conducted part of the computational experiments. MR designed and implemented the listening tests. GL designed the listening tests and provided guidance in the design of the computational experiments. JA provided guidance in the design of the computational experiments, participated to the data analysis and  to the writing of the manuscript. ML designed and conducted the computational experiments, the data analysis and participated to the writing of the paper.

>>>>

We see from the ablation study conducted above that each step of the proposed model is necessary for its high performance.
Among other things, it indicates the joint time--frequency scattering transform itself should not be used directly for similarity comparisons, but is best augmented by a learned stage.
This explains the relative success of such models \cite{lostanlen2018jasmp,lostanlen2018extended} over others where distances on raw scattering coefficients were used for judging audio similarity.

@@

VL provided guidance in the design of the computational experiments and was a major contributor in writing the manuscript. CEH conducted part of the computational experiments. MR designed and implemented the listening tests. GL designed the listening tests and provided guidance in the design of the computational experiments. JA provided guidance in the design of the computational experiments, participated to the data analysis and  to the writing of the manuscript. ML designed and conducted the computational experiments, the data analysis and participated to the writing of the paper.
